Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
some systematic words

The method of \paperit assumes that all variability in the light curves are
caused by either the motion of \KT, in which case the variability is shared
by all stars, or transits of planets, in which case the variability is intrinsic 
to only one star.
This assumption breaks down for extremely spotted stars where the 
astrophysical variability is larger than the instrumental
magnitude.
In that regime, the starspot modulations can be incorrectly fit by the 
systematic model, causing spurious transits to appear.
This appears to be the case with EPIC 201929294, which has 
coherent starspots that appear to have the same rotation period as the
transit period reported previously.
Because the starspots are so periodic and coherent, these spurious 
transits were falsely identified as a planet candidate; we consider that 
system a false positive in this work.

The planet candidate possibly orbiting EPIC 201555883 has a period, 
time of transit, and transit duration consistent with EPIC 201569483.
Such effects are not uncommon in \kep\ data.
\citet{Coughlin14} identify 685 KOIs as false
positives and outline four physical reasons why these anomalies may occur.
EPIC 201555883 is a unique case in that it does not appear to fall under any
of these cases. It falls on module 23, while EPIC 201569483 is on module 8,
neither 180 degrees away from nor on the same column as this candidate.
Moreover, there is not any evidence of a mechanism that could cause a third
star to induce both the appearance of a $7\%$ eclipse on one module and an
additional anomalous transit event on a different module.
Instead, this candidate could be a false positive caused by a different
systematic mechanism.
\paperit\ modeled the systematic effects in the \KT\ light curves using a
linear combination of ``eigen light curves'' generated empirically by running
a principle component analysis on the light curves of every star.
This means that the training set includes the light curves for variable stars,
eclipsing binaries, and even transiting planets.
In this specific case, the s

>>>>

The method of \paperit\ assumes that all variability in the light curves are
caused by either the motion of \KT, in which case the variability is shared
by all stars, or transits of planets, in which case the variability is intrinsic 
to only one star.
This assumption breaks down for extremely spotted stars where the 
astrophysical variability is larger than the instrumental
magnitude.
In that regime, the starspot modulations can be incorrectly fit by the 
systematic model, causing spurious transits to appear.
This appears to be the case with EPIC 201929294, which has 
coherent starspots that appear to have the same rotation period as the
transit period reported previously.
Because the starspots are so periodic and coherent, these spurious 
transits were falsely identified as a planet candidate; we consider that 
system a false positive in this work.

The planet candidate possibly orbiting EPIC 201555883 has a period, 
time of transit, and transit duration consistent with EPIC 201569483.
Such effects are not uncommon in \kep\ data.
\citet{Coughlin14} identify 685 KOIs as false
positives and outline four physical reasons why these anomalies may occur.
EPIC 201555883 is a unique case in that it does not appear to fall under any
of these cases. It falls on module 23, while EPIC 201569483 is on module 8,
neither 180 degrees away from nor on the same column as this candidate.
Moreover, there is not any evidence of a mechanism that could cause a third
star to induce both the appearance of a $7\%$ eclipse on one module and an
additional anomalous transit event on a different module.
Instead, this candidate could be a false positive caused by a different
systematic mechanism.

\paperit\ modeled the systematic effects in the \KT\ light curves using a
linear combination of ``eigen light curves'' generated empirically by running
a principle component analysis on the light curves of every star.
This means that the training set includes the light curves for variable stars,
eclipsing binaries, and even transiting planets.
Again, this star has significant variability caused by starspots. 
In this case, the fitting procedure tries to account for stellar variability using
the eigen light curves.
This overfit gives undue weight to eigen light curves that include the transits
of EPIC 201569483, causing this spurious transit to occur.
Again, we consider this system to be a false positive.

The problem of over-fitting stellar variability using eigen light curves can be
solved by adding a stellar activity model to our fitting procedure.
In this case, the spacecraft motion could be fit simultaneously with a model
of starspot modulation, astroseismic oscillations, and planet transits.
Such a model is currently under development (Angus et al. \textit{in prep}).
